---
title: "Course Report"
author: "Francis Biney"
date: "May 2022"
output:
#  html_notebook: default
#  pdf_document: default
  bookdown::pdf_document2: default
  bookdown::html_document2: default
bibliography: ref.bib
biblio-style: apalike
link-citations: yes
fig_caption: yes
---



```{r, echo = FALSE}
setwd("C:/Users/fbiney/Desktop/WaterProj/Coures-Report_1/Code_Report")

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r, include= FALSE}

# LIBRARIES----
# Load Library----
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(skimr)
library(funModeling)
library(gtsummary)
library(DataExplorer)
library(visdat)

#library('tigris') # Census data manip.
#options(tigris_use_cache = TRUE) # make download faster

```


```{r, include=FALSE}
source("data.R", local = knitr::knit_global())
```


# Introduction

In this work, we explore the distribution, correlations and effect of
lead and wastewater exposure in El Paso communities (census tracts) using
geospatial heat maps and data obtained from the Climate and Economic Justice Screening Tool
(CEJST) initiative [website](https://screeningtool.geoplatform.gov/en/about). The CEJST tool is a Biden-Harris
Administration's project to help address inequity and inequality by
assisting federal agencies in identifying disadvantaged communities that
are marginalized, underserved, and overburdened by pollution
[(CEJST 2022)](https://www.federalregister.gov/documents/2021/02/01/2021-02177/tackling-the-climate-crisis-at-home-and-abroad#:~:text=Sec.%20223.%20Justice40,40-percent%20goal.). We also provided feedback on features that we thought were
great, features that we would like to see, and roadblocks we encountered
while implementing the Climate and Economic Justice Screening Tool (CEJST)in its
beta phase from github.

# Exploration of CEJST for EL Paso county.

Figure 1 shows the CEJST result for a community in El Paso with zip code
79968. It contains information such as the census tract id, the county,
state, population, and whether or not the the community is classified as
disadvantaged. The community is identified as not disadvantaged because
it was not disadvantaged in any of the eight categories.

![**Screening tool for Zip code 79938 in ElPaso
**](C:%5CUsers%5Cfbiney%5CDesktop%5CWaterProj%5CCourseReport_new%5CElpasoCejt2.PNG)

[CEJST Tool](https://screeningtool.geoplatform.gov/en/#9.89/31.812/-106.4175)

# Summary of CEJST Tool

In this section, we provide a summary of what we would like to see, the
features we thought were great, and the roadblocks we encountered during
the Climate and Economic Justice Screening Tool implementation process (CEJST).

### Feed back on what can be improved

To better analyze, understand and respond to the need of communities,
here are the feature we will like to see in the application:

1.  A filter that allows users to change the binary scale (disadvantage
    or not ) to a discrete scale $(0,1, …,8)$, where 0 means not
    disadvantaged, 1 means least disadvantage and 8 means most
    disadvantaged community, that is disadvantaged in all 8 categories.
    This will allow the user to easily identify highly disadvantaged
    communities when prioritizing funding.

2.  A filter that allows users to filter by categories such as water
    infrastructure within a county. This will help users to know which
    communities(census tract) are most affected by a given category. For
    example, if a user wants to prioritize funding for water
    infrastructure she/he should be able to filter to see which tracts
    in the community are affected. This will also help community groups
    to better understand the different types of challenges they face and
    the type of funding they should apply for.

3.  The data used for the Economic injustice analysis did not include
    race/ethnicity. I believe there is an association between the
    dominant race in a community and their health, environmental and
    socioeconomic needs. The analyses and application will be more
    informative if the race data is included.

4.  To better understand the effect of lead on communities, information
    on lead pipes use in the communities need to be included and be used
    in the analysis not only lead paint.

5.  A button to display/highlight the effect on health measures and life
    expectancy of a disadvantaged community given the category. For
    example, what is the general life expectancy for people in the
    community given their lead exposure level?

6.  Provide code snippets or interactive applets that allow non-tech
    users to explore their own questions on different data.

### Point of Implimenttion

On the implementation of the Climate and Economic Justice Screening Tool (CEJST) in
its beta stage from Github, here are our roadblocks:

1.  The installation of the application from the Github repository is
    not user-friendly, and non-tech users will find it hard or almost
    impossible to get the application to work. it requires a lot of
    technical know-how and youtube time. It took me about a week to get
    the application to run on my local computer.

2.  To get the application to run on my local computer

    a.  Install git on my windows computer

    b.  Clone (copy) the directory (folder) from Github to my local
        computer

    c.  Install docker on windows

        i.  Install/Set up WSL2 (windows subsystem for linux 2)
        ii. Install Ubuntu on Windows
        iii. Download and install docker

## 

Finally, here are the features we liked and thought were great. The
application was intuitive to use once the installation was done. A good
description of the methodology and data used is available on the
localhost. This allowed for answering further questions that were not
addressed in the application. On the technical end, I appreciated the
opportunity to install and run Docker for the first time. This has given
me the experience to work in a similar framework in the future

# Research Question (What we Did)

-   Where in El Paso (census tract) has higher percentage of lead paint exposure.

-   Where in El Paso (census tract) has higher percentage wastewater discharge
    exposure.

-   What is the effect of higher percentage of lead paint exposure on health
    of the El Paso community.

-   What is the effect of higher percentage of wastewater discharge exposure on
    health of El Paso community.

# Literature Review

Lead pollution has been shown to be especially harmful in low-income
neighborhoods and communities of color, according to the Center for
Disease Control
[(CDC, 2021)](https://www.cdc.gov/nceh/lead/prevention/populations.htm).
Children who live in lower income neighborhoods or communities of color
are more likely to be exposed to lead based paint, dust, or soil than
their higher income peers. These exposures have devastating effects on
the growth and development of children's brains, and have been linked to
behavioral issues such as attention deficit hyperactivity disorder
ADHD [@needleman1982lead], poor school performance[@kuang2020adverse], poor memory[@arnvig1980neurotoxic],
lower IQ scores[@needleman1990low], and reduced life expectancy in
adults[@sandhya2016impact].

Paso del Norte community in El Paso, Texas is known to have a high concentration of lead in the air and
soil[@darby2012lead]. This is due to heavy metal contamination caused by the
extraction of lead, copper, and zinc from metal ore by the American
Smelting and Refining Company (ASARCO) [@marcosson1949metal] from 1901 to
1999, which was acquired by Grupo Mexico in 2009 and closed in 2009.
[@darby2012lead]. Lead and arsenic persist in the region's soils
[@alvarez2015comparison] and perhaps in people's bodies, ground, and surface
water, despite the fact that the smelter is no longer in operation.

Residents and regulatory agencies have focused on these two pollutants
due to their health effects on children and the environment.

Mielke and Reagan [@mielke1998soil] showed that lead is particularly troubling due
to its propensity to settle in the soil, where it can be inhaled or
ingested by humans. Long-term lead exposure reduces cognitive
functioning, which can influence educational outcomes and economic
opportunities [@schell1997culture]. 


# Methodology

Here we discuss the methods we used to answer these question. We focused
on exploring the distribution, correlation and association between water
quality related measures such as exposure to lead paint, exposure to
wast water discharged and basic demographic measures including education
level, socio-economics status, and health related measures such as
percent adult diagnose Diabetes,Asthma, 
Heart disease and life expectancy in the El Pose community. We did this
using Numerical and graphical summaries such as box plot conditional bar
graphs, Stacked bar Chart, mosaic plot and geospatial heat maps. The
goal was to understand the effect of exposure to high lead pain and
water waste disposal have on disadvantage communities.

# Statistical Analyses

## Data

The data use is available on the Climate and Economic Justice Screening
Tool (CEJST)
[website](https://screeningtool.geoplatform.gov/en/methodology) under
methodology and data page, published on March 30,2022. The data contain
74131 observations(rows) and 83 variables(Columns) with information on
environmental, climate and socio-economic related measures. The measures
include activities that adversely impact human health, climate and the
environment such as use of lead paint, Traffic proximity, Proximity to
hazardous waste site, diesel particulate matter exposure. It also has
data on health related measures such as heart disease, asthma, diabetes
and socio-economic measures such as low income, Unemployment, Poverty
rate and higher education enrollment rate.The target variable contains
information on whether or not a community is disadvantage based on the
criterior below. The (CEJST)
[team](https://static-data-screeningtool.geoplatform.gov/data-pipeline/data/score/downloadable/cejst_technical_support_document.pdf)
defined a community qualifies as disadvantaged if

1.  the U.S. census tract is above the threshold for one or more
    environmental or climate indicators, and
2.  the U.S. census tract is above the threshold for the socioeconomic
    indicators.

These categories and threshold can be found on the (CEJST)
[website](https://screeningtool.geoplatform.gov/en/methodology).
Additional goeospatial data was obtained from the [*tigris
package*](https://github.com/walkerke/tigris) in R, which was combined
with (CEJST) data to create the El Paso map with the census tract. Below
is first eight observations and columns in the data.




```{r echo=FALSE, message=FALSE, warning=FALSE}
#dim(dat1)
#dat1 %>% head(10)
#dat1 %>% select(1:8) %>% head(8)
#skim(dat)
library(knitr)
dat1 %>% select(1:8) %>% head(8) %>% kable()
```

### Data Processin and Feature Enginerring

The original data came from multiple source with long columns name so we
gave the variable a shorter name. This was done using the *janitor
package* in *R*. We then explore the 83 columns for water quality and
basic demographics related measures such as lead and wasted water,
income, Education level. El Paso county data was subset form the 74131
original observations to 161.


**Missing values Treatment**

Very few observations $(3.1\%)$ were missing,so we dropped them from the
data. Wastewater discharged, life expectancy and media house hold
income have most missing values ranging from $27\%,11.4\%$ and $6.2\%$
respectively as shown in the figures 2 and 3 below.


```{r fig1,echo=FALSE, message=FALSE, warning=FALSE,fig.cap="plotting example"}
# Plot the structure of the data 
plot_intro(dat2, title = "Structure of the Data")

```

in Figure \@ref(fig:fig1) we see examples of plotting in R





```{r cars-plot, fig.cap="A plot caption"}
plot(cars)  # a scatterplot
```


in Figure \@ref(fig:cars-plot) we see examples of plotting in R




```{r , echo=FALSE,message = FALSE, warning=FALSE}
#library(visdat)
vis_miss(dat2,warn_large_data = FALSE) # explore the missing data
```

**Feature Engineering**

The logical variables *Lead.Paint*,*Proximity to hazard waste site* and
*Proximity to wastewater discharged* were re-coded as binary factor
with categories *(yes,no)* for *(True,false)* respectively for modeling
purpose.

### Data Exploration and Summary

**Water quality data**

We performed exploratory data analysis on the El Paso data to understand
the the distribution, correlations and association between the water
quality and demographics variables. This was done by inspecting the data
distribution for skewness, outliers, trends and also summarize the data
into it main characteristics. From table **[??]**, about 63% of El Paso
census tract were classified as disadvantaged communities and 37%
not by the CEJST formula (CEJST 2022) for deciding  disadvantage communities. 
Table **[??]** below show that 5% of El Pasoans live in
lead painted house ,24% close to wastewater discharge area and none
close to Hazard waste site. This also shown in  figure **[??]**...blue color. The
distribution of the wastewater contain mostly high values.



```{r,fig.height=3, fig.width=7,message=FALSE, warning=FALSE, echo=FALSE}
#fig.height=3, fig.width=10,

p1<-EP_WQ_df %>% ggplot(aes(x=is_disAdvan,fill= is_disAdvan))+
  geom_bar() +labs(x = "Disadvantage") +theme(legend.position="none")

p2<-EP_WQ_df %>% ggplot(aes(x=Ld.Paint.gde90_LILE,fill= Ld.Paint.gde90_LILE))+
  geom_bar()+labs(x = "Lead Paint >= 90%") +theme(legend.position="none")

p3<-EP_WQ_df %>% ggplot(aes(x=prox.hazard.waste.facilit_gde90_LILE,fill= prox.hazard.waste.facilit_gde90_LILE))+
  geom_bar()+labs(x = "Prox.Hazard waste site") +theme(legend.position="none")


p4<-EP_WQ_df %>% ggplot(aes(x=wastewater.dischg.gde90_LILE,fill= wastewater.dischg.gde90_LILE))+
  geom_bar()+labs(x = "Wastewater discharge >= 90%")+      
  theme(legend.position="none")

ggpubr::ggarrange(p1,p2,p4,nrow = 1,ncol = 3)

#gridExtra::grid.arrange(p1,p2,p3,p4)

```

```{r,echo=FALSE,message = FALSE}

EP_WQ_df %>% 
  select(is_disAdvan,Ld.Paint.gde90_LILE,prox.hazard.waste.facilit_gde90_LILE,wastewater.dischg.gde90_LILE) %>% 
  rename( 'Disadvantage' = is_disAdvan,
          'Lead Paint'= Ld.Paint.gde90_LILE,
          'Wastewater discharge >= 90%'=wastewater.dischg.gde90_LILE,
          'Prox. to Harzd. site'=prox.hazard.waste.facilit_gde90_LILE
          ) %>% 
 tbl_summary() %>% 
 bold_labels() %>%
 add_n() %>%
 modify_header(stat_0 ~ "**n(%)**") 
```

```{r , echo=FALSE, warning=FALSE,message = FALSE,fig.height=3, fig.width=7}
EP_WQ_df %>% 
  select(Ld.paint.1960.ptil,prox.hazard.waste.site.ptil,wastewater.dischg.ptil) %>% 
  rename( 'Lead Pain' = Ld.paint.1960.ptil,
          'Prox. to Hazard Waste site'= prox.hazard.waste.site.ptil,
          'Wastewater dischgarge'=wastewater.dischg.ptil ) %>% 
  plot_num()
```

```{r,echo=FALSE,message = FALSE}
EP_WQ_df %>% 
  select(Ld.paint.1960.ptil,prox.hazard.waste.site.ptil,wastewater.dischg.ptil) %>% 
  rename( 'Lead Pain Exp. > 90th' = Ld.paint.1960.ptil,
          'Prox. to Hazard Waste site'= prox.hazard.waste.site.ptil,
          'Wastewater dischgarge'=wastewater.dischg.ptil ) %>% 
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = all_continuous() ~ c(#"{N_nonmiss}",
                                     "{mean} ({sd})", 
                                     "{median} ({p25}, {p75})"),
  ) %>% 
  add_n() %>% 
  modify_header(stat_0 ~ "**Statistics**") %>% 
  bold_labels()

```

**Demographics and Health Data**

Table[]and Figure[], shows the summary statistics and distribution
of El Paso demographic and health related data. From table[], about
69% and 23% of the of the adult in the census tract are diagnose with
diabetes and heart disease respectively.

```{r,echo=FALSE,message = FALSE}
  Demo_df %>% 
  select(
  #total_population, 
  life.expectcy_yrs,
  Diabetes.gde90_LILE,  
  Heart.dis.gde90_LILE,
  Diabetes.Adults.age18.diag.ptil,
  Heart.dis.Adults.age18.ptil,
  #unemplt.p.ptil
) %>% 
rename(
       #'Total population' = total_population,
       'Life Expectancy Yrs.' = life.expectcy_yrs,
       #'Unemploymnet Percentile' = unemplt.p.ptil,   
       'Diabetes'   = Diabetes.gde90_LILE, 
       'Heart disease'  = Heart.dis.gde90_LILE,
       'Diabetes Percentile'  = Diabetes.Adults.age18.diag.ptil,           
       'Heart disease Percentile' = Heart.dis.Adults.age18.ptil               
                               
) %>%   
tbl_summary(
  type = all_continuous() ~ "continuous2",
   statistic = all_continuous() ~ c(#"{N_nonmiss}",
                                     "{mean} ({sd})", 
                                     "{median} ({p25}, {p75})")
) %>% 
add_n() %>% 
modify_header(stat_0 ~ "**Statistics**") %>% 
bold_labels()

```

```{r, echo=FALSE, warning=FALSE,message = FALSE,fig.height=3, fig.width=7}
EP_Demo_df %>% 
  select(
         life.expectcy_yrs,
         Diabetes.gde90_LILE,
         Heart.dis.gde90_LILE,
         Diabetes.Adults.age18.diag.ptil,
         Heart.dis.Adults.age18.ptil) %>% 
rename('Diabetes'   = Diabetes.gde90_LILE,
       'Life Expectancy Yrs.' = life.expectcy_yrs,
       'Heart disease'  = Heart.dis.gde90_LILE,
       #'Unemploymnet Percentile' = unemplt.p.ptil,  
       'Diabetes Percentile'  = Diabetes.Adults.age18.diag.ptil,           
       'Heart disease Percentile' = Heart.dis.Adults.age18.ptil               
                               
)  %>% 
  plot_num()
```

```{r, echo=FALSE,message = FALSE,fig.height=3, fig.width=7}

p1<-EP_Demo_df %>% ggplot(aes(x=Diabetes.gde90_LILE,fill= Diabetes.gde90_LILE))+
  geom_bar() +labs(x = "Diabetes") +theme(legend.position="none")

p2<-EP_Demo_df  %>% ggplot(aes(x=Heart.dis.gde90_LILE,fill= Heart.dis.gde90_LILE))+
  geom_bar()+labs(x = "Heart disease") +theme(legend.position="none")

p3<-EP_Demo_df  %>% ggplot(aes(x=Low.life.expectcy.gde90_LILE,fill= Low.life.expectcy.gde90_LILE))+
  geom_bar(size=2)+labs(x = "LLE") +theme(legend.position="none")



ggpubr::ggarrange(p1,p2,p3,nrow = 1,ncol = 3)


```

# Application and Result

## Visualization of Texas County and El Paso census Tract

```{r echo=FALSE}
plot(tx_county["NAME10"],main = "Texas County Map")
plot(tx_tract["NAME10"],main = "El Paso Census tract")
```

## Visualizing Disadvantage Community(tract) by CEJST criterion

To understands which communities in El Paso are disadvantaged by (CEJST)
criterion we made geospatial heat maps for El Paso census tract, showing
whether the tract is a disadvantage or not. From table [], about 63%
of El Paso communities are disadvantage *blue below*. Here a community
identified as disadvantaged if disadvantaged in at least one of the
eight categories
[CEJST 2022](https://screeningtool.geoplatform.gov/en/methodology#:~:text=Under%20the%20current,the%20socioeconomic%20indicators).

```{r echo=FALSE}
# Dis Adv or Not vs tract   ----------------------------
g1<-ggplot(WQ_tract_tbl, aes(fill = is_disAdvan)) + 
  geom_sf()+
  labs(title='Disadvantage vs Non-Disadv. In EL Paso')


g1 + scale_fill_discrete(name="Disadvantage")

```

To highlight El Paso communities that are most disadvantaged we create a
heat map with 0 meaning not disadvantaged, 1- least disadvantage and 8
means most disadvantaged community.

```{r echo=FALSE}
# Total_categories Exceeded vs vs tract   ------
g2 <- ggplot(WQ_tract_tbl, aes(fill = T_cat_exceded)) + 
  geom_sf()+
  #scale_fill_gradient(low='#56B1F7',mid=high = '#132B43')
  scale_fill_gradient2(low='blue',mid='white',high = 'red',name="Total Categories Exceeded")+
  labs(title='Total Categories Exceeded')

g2
  
```

## Visualizing Communities with water quatlity problem

**Lead paint Exposure**

```{r echo=FALSE}
# High % Lead paint vs tract --------

g3<-ggplot(WQ_tract_tbl, aes(fill = Ld.Paint.gde90_LILE)) + 
  geom_sf()+
  labs(title='El Paso Communities with and without lead Pain Exposure')


g3+ scale_fill_discrete(name="Lead Exposure")

#----bY------------
#library(mapview)
#mapview(WQ_tract_tbl,zcol="Ld.Paint.gde90_LILE")

```

**wastewater Exposure**

```{r echo=FALSE}
# wastewater Dischr vs tract ----------------------------

g4<-ggplot(WQ_tract_tbl, aes(fill = wastewater.dischg.gde90_LILE  )) + 
  geom_sf()+
  labs(title='El Paso Communities with and without wastewater Exposure',
       caption = "FIGURE 10")

g4+ scale_fill_discrete(name="wastewater Exposure")



#----bY------------
#mapview(WQ_tract_tbl,zcol="wastewater.dischg.gde90_LILE")
```

## Effect of high% lead Piant Exposure

The box plots in Figure 0 below show significant differences in medical
conditions between whether communities live in lead-painted houses or
not. From the box plots, communities that live in lead-painted houses
have a high number of adults diagnosed with diabetes, heart disease and
have low life expectancy.

```{r message=FALSE, warning=FALSE, include=FALSE}
library(ggpubr)

EP_WQ_Demo_df <- EP_Demo_df %>% 
  mutate(Lead = EP_WQ_df$Ld.Paint.gde90_LILE)




p1 <- EP_WQ_Demo_df %>% 
  ggplot(aes(x=Lead,y=life.expectcy_yrs ,fill=Lead))+
  geom_boxplot() + labs(y = "Life Expect. Yrs.") +theme(legend.position="none")


p2<- EP_WQ_Demo_df %>% 
  ggplot(aes(x=Lead,y=Diabetes.Adults.age18.diag ,fill=Lead))+
  geom_boxplot()  + labs(y = "Adult diagnosed diabetes") +theme(legend.position="none")




p3<- EP_WQ_Demo_df %>% 
  ggplot(aes(x=Lead,y= Heart.dis.Adults.age18    ,fill=Lead))+
  geom_boxplot() + labs(y = "Adullt diagnosed heart disease.") +theme(legend.position="none")


plt<- ggarrange(p2,p3,p1, ncol=3, nrow=1, common.legend = TRUE,legend="bottom")

```

```{r echo = FALSE}
annotate_figure(plt, top = text_grob("Lead's effect Medical on Condition", 
               color = "black", face = "bold", size = 14),
               fig.lab = "FIGURE 0", fig.lab.face = "bold")
               
```

## Effect of high% wastewater discharge on life Expectancey, Diabetie and Heart Disease

The box plots in Figure 1 below show significant differences in medical
conditions between communities living near wastewater discharge and
communities far from wastewater discharge. From the box plots,
communities that live close to wastewater discharge have a high number
of adults diagnosed with diabetes, heart disease, and low life
expectancy.

```{r message=FALSE, warning=FALSE, include=FALSE}


EP_WQ_Demo_df <- EP_Demo_df %>% 
  mutate(Lead = EP_WQ_df$Ld.Paint.gde90_LILE,
         'wastewater' = EP_WQ_df$wastewater.dischg.gde90_LILE)



pp1 <- EP_WQ_Demo_df %>% 
  ggplot(aes(x=`wastewater`,y=life.expectcy_yrs ,fill=`wastewater`))+
  geom_boxplot() + labs(y = "Life Expect. Yrs.") +theme(legend.position="none")


pp2<- EP_WQ_Demo_df %>% 
  ggplot(aes(x=`wastewater`,y=Diabetes.Adults.age18.diag ,fill=`wastewater`))+
  geom_boxplot()  + labs(y = "Adult diagnosed diabetes") +theme(legend.position="none")




pp3<- EP_WQ_Demo_df %>% 
  ggplot(aes(x=`wastewater`,y= Heart.dis.Adults.age18    ,fill=`wastewater`))+
  geom_boxplot() + labs(y = "Adullt diagnosed heart disease.") +theme(legend.position="none")


plt2<- ggarrange(pp2,pp3,pp1, ncol=3, nrow=1, common.legend = TRUE,legend="bottom")


```

```{r echo = FALSE}
annotate_figure(plt2, top = text_grob("wastewater's effect Medical on Condition", 
               color = "black", face = "bold", size = 14),
               fig.lab = "FIGURE 1", fig.lab.face = "bold")

```

# Conclusion 
This work explores the distribution, correlation, and effect of exposure to lead and wastewater on heart disease, diabetes, and life expectancy in El Paso communities. We accomplished this by using geospatial heat maps, boxplot, data from the CEJST initiative, and the Tigris package for CRAN. 

In our exploration and analysis, we observed that communities with high exposure to lead and wastewater tend to have a higher number of people diagnosed with diabetes and heart disease. These communities also have low life expectancies relative to unexposed communities. We also observed that most communities with high lead exposure also have high wastewater exposure.

# Suggestion

The analysis will be more informative if communities with lead pipes are included in the data. Other suggestions include:

-   Statistical Analysis to justify whether a significant difference exists between the groups compared

-   Model the $above.90th.percentile.PM2.5$ using binomial logit model with other columns as predictors.


-   Model the $above.90th.percentile.lead.paint.exposure$ using binomial logit model with other columns as predictors.


-   Find features that are top predictors of disadvantageous communities.

-   Model the $Total.categories.exceeded$ using the proportional odds model.




# Reference



